Mental Rotation as Bayesian Quadrature

### 2013-10-17 man/nips-2013-bayesian-optimization.tex
Split caption into subcaptions

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/model_rotations_A.pdf}
    % \vspace{0pt}
    \caption{All stimuli}
    \label{fig:all-stimuli}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/model_rotations_B.pdf}
    \caption{Correct stimuli}
    \label{fig:correct-stimuli}
  \end{subfigure}
  \caption{\textbf{Model rotations.} (a) Each subplot shows the
    correspondence between the true angle of rotation ($R$) for
    ``same'' pairs and the amount of rotation performed by the
    model. (b) Each subplot shows the models' mean rotations over
    stimuli pairs that were judged correctly. Black dots correspond to
    ``same'' pairs, and blue lines correspond to ``different''
    pairs. Error bars/shaded regions indicate one standard deviation,
    and the dotted lines indicate the least-squares fit to the
    ``same'' pairs.}
  \label{fig:rotations}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/model_rotations_A.pdf}
    \caption{\textbf{All stimuli}. Each subplot shows the
      correspondence between the true angle of rotation ($R$) for
      ``same'' pairs and the amount of rotation performed by the
      model.}
    \label{fig:all-stimuli}
  \end{subfigure}
  \hspace{0.05\textwidth}
  \begin{subfigure}[b]{0.46\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/model_rotations_B.pdf}
    \caption{\textbf{Correct stimuli}. Each subplot shows the models'
      mean rotations over stimuli pairs that were judged
      correctly. Black dots correspond to ``same'' pairs, and blue
      lines to ``different'' pairs.}
    \label{fig:correct-stimuli}
  \end{subfigure}
  \caption{\textbf{Model rotations.} Error bars/shaded regions
    indicate one standard deviation, and the dotted lines indicate the
    least-squares fit to the ``same'' pairs.}
  \label{fig:rotations}
\end{figure}
